Labor Market Income and Substitution Effects Explain Contemporary Natural Selection

### 2020-12-16 why-negative-selection.Rmd
More tweaks.

options(digits = 2)
options(dplyr.summarise.inform = FALSE) # shut up about summarize
knitr::opts_chunk$set(
        echo = FALSE, 
        warning = FALSE, 
        cache = FALSE, 
        error = TRUE,
        fig.height = 3.5
      )

@@

ineq_comp %<>% mutate(
                 diff_children = wtd.y - wtd.x,
                 diff_hypoth   = unw.y - unw.x
               )

ineq_comp %>% 
      select(
        PGS                 = score, 
        `With selection`    = diff_children, 
        `Without selection` = diff_hypoth
      ) %>% 
      mutate(
        PGS = pretty_names(PGS)
      ) %>% 
      arrange(desc(`With selection`)) %>% 
      as_hux() %>% 
      set_align(everywhere, -1, "right") %>% 
      set_number_format(everywhere, -1, 3) %>% 
      set_caption("Differences in polygenic scores between highest and lowest income group.") %>% 
      theme_compact() %>% 
      set_bottom_border(final(1), everywhere)
```

>>>>

options(digits = 2)
options(dplyr.summarise.inform = FALSE) # shut up about summarize
knitr::opts_chunk$set(
        echo = FALSE, 
        warning = FALSE, 
        cache = FALSE, 
        error = TRUE,
        fig.height = 3.5
      )
options(huxtable.long_minus = TRUE)

@@

ineq_comp %<>% mutate(
                 diff_children = wtd.y - wtd.x,
                 diff_hypoth   = unw.y - unw.x,
                 pct_change    = 100 * (diff_children - diff_hypoth)/diff_hypoth
               )

ineq_comp %>% 
      select(
        PGS                 = score, 
        `Without selection` = diff_hypoth,
        `With selection`    = diff_children, 
        `% change`          = pct_change
      ) %>% 
      mutate(
        PGS = pretty_names(PGS)
      ) %>% 
      arrange(desc(`% change`)) %>% 
      as_hux() %>% 
      set_align(everywhere, -1, "right") %>% 
      set_number_format(everywhere, 2:3, 3) %>% 
      set_number_format(everywhere, 4, 1) %>% 
      set_caption("Differences in polygenic scores between highest and lowest income group.") %>% 
      theme_compact() %>% 
      set_bottom_border(final(1), everywhere)
```
